---
title: "Final Project-Group 2"
author: "Thanh Nguyen,Hannah Wang, Lu Qiu"
date: "May 01, 2017"
output:
  html_document: default
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Main Question and Objective
Main question: "Is it possible to predict a movie profit prior to its release based on certain characteristics?"

### Question Development
Our model was developed based on a similar but simpler model that some of us worked on previously. The data was collected from all movies shown in the theathers in 2012 (n=30) with 8 variables and 3 were selected into the model. Since the sample size was small for the previous project, we wanted to create a better model to predict movie gross sales from a larger sample with more parameters.

Given the high popularity of predictions of how well movies would do in box office, some based purely on author's opinions, some actually created a model from differen data sources, we wanted to create a uniform model that would be available for everyone to use.

### Data Gathering
Our very first approach was to scrap all available movie data from http://www.boxofficemojo.com/. However, we decided that this wasn't doable given the limited time that we had for our project. We then did our research and found the movie dataset that was published on Kaggle. The data was in a readable format and had the information that we were looking for in order to create our prediction model.

### Preparing Data for analysis

Below are the steps that were used to prepare our data for analysis.
#### Import Data

```{r}
#Import Dataset
moviedata <- data.frame(read.csv("movie_metadata.csv"))
```

#### Initial Exploratory Data Analysis

```{r}
#### Problem 1 -- many NA values
#### Problem 2 -- too many categorical variables and each have many categories
#### Problem 3 -- many variables may have severe multicolinearity

head(moviedata)
str(moviedata)
summary(moviedata)

#### Problem 4 -- many duplicate rows

#123 movies are duplicated, have the same movie_title and plot_keywords
index1 <- duplicated(moviedata[,"movie_title"])
index2 <- duplicated(moviedata[,"plot_keywords"])
index <- index1 & index2
sum(index)

#### Problem 5 -- skewness in gross data

#Since we want to use gross income as our dependent variable, we need to do some test to see  if it is normally distributed. 
hist(moviedata$gross, main="Histogram of movie gross sale")
shapiro.test(moviedata$gross)
#Look like we have a right skewed dataset.

```

Based on the initial exploratory Data Analysis, we conducted the following data cleaning, feature engineering, and feature selection processes.

#### Data cleaning step 1  -- delete duplicate rows

```{r}
#delete the duplicate rows according to movie title and plot keywords
index1 <- duplicated(moviedata[,"movie_title"])
index2 <- duplicated(moviedata[,"plot_keywords"])
index <- index1 & index2
moviedata <- moviedata[!index,]
```

#### Data cleaning step 2  -- delete NA gross and entries

```{r}
#Since want want to use gross as our dependent variable, we needed to obmit all entries that have NA for gross
moviedata <- moviedata[!is.na(moviedata$gross), ]
nrow(moviedata)

#It was surprising to find that our data had so many 0 gross data.This was either caused by (a) no gross number was found in certain movie page, or (b) the response returned by scrapy http request returned nothing in short period of time. We may also need to delete those rows.
moviedata <- moviedata[moviedata$gross != 0,]
summary(moviedata$gross)
nrow(moviedata)

#The min of gross is 162, no negative value, no zero.
```

#### Data cleaning step 3 -- use mean value to replace missing value of numerical features

```{r}
moviedata$imdb_score[is.na(moviedata$imdb_score)] <- mean(moviedata$imdb_score,na.rm = TRUE)
moviedata$budget[is.na(moviedata$budget)] <- mean(moviedata$budget,na.rm = TRUE)
moviedata$duration[is.na(moviedata$duration)] <- mean(moviedata$duration,na.rm = TRUE)
moviedata$director_facebook_likes[is.na(moviedata$director_facebook_likes)] <- mean(moviedata$director_facebook_likes,na.rm = TRUE)
moviedata$num_critic_for_reviews[is.na(moviedata$num_critic_for_reviews)] <- mean(moviedata$num_critic_for_reviews,na.rm = TRUE)
moviedata$actor_3_facebook_likes[is.na(moviedata$actor_3_facebook_likes)] <- mean(moviedata$actor_3_facebook_likes,na.rm = TRUE)
moviedata$actor_1_facebook_likes[is.na(moviedata$actor_1_facebook_likes)] <- mean(moviedata$actor_1_facebook_likes,na.rm = TRUE)
moviedata$num_voted_users[is.na(moviedata$num_voted_users)] <- mean(moviedata$num_voted_users,na.rm = TRUE)
moviedata$cast_total_facebook_likes[is.na(moviedata$cast_total_facebook_likes)] <- mean(moviedata$cast_total_facebook_likes,na.rm = TRUE)
moviedata$facenumber_in_poster[is.na(moviedata$facenumber_in_poster)] <- mean(moviedata$facenumber_in_poster,na.rm = TRUE)
moviedata$num_user_for_reviews[is.na(moviedata$num_user_for_reviews)] <- mean(moviedata$num_user_for_reviews,na.rm = TRUE)
# need to consider later
moviedata$title_year[is.na(moviedata$title_year)] <- mean(moviedata$title_year,na.rm = TRUE)
moviedata$actor_2_facebook_likes[is.na(moviedata$actor_2_facebook_likes)] <- mean(moviedata$actor_2_facebook_likes,na.rm = TRUE)
moviedata$imdb_score[is.na(moviedata$imdb_score)] <- mean(moviedata$imdb_score,na.rm = TRUE)
moviedata$aspect_ratio[is.na(moviedata$aspect_ratio)] <- mean(moviedata$aspect_ratio,na.rm = TRUE)
moviedata$movie_facebook_likes[is.na(moviedata$movie_facebook_likes)] <- mean(moviedata$movie_facebook_likes,na.rm = TRUE)
```

#### Data cleaning step 4  -- transform continuous variable to log(x) format to avoid skewness

```{r}
#Transformed it to log(x) format, much better in histagram, but still have skewness
moviedata$gross = log(moviedata$gross)
hist(moviedata$gross, main = "Histogram of movie gross sale")
shapiro.test(moviedata$gross)
```

#### EDA-Part 2 -- After data cleaning is done, we wanted to see if there was any correlation between gross and other variables (continous variables only)
```{r}
#### Correlation -- we want to do the initial check to see if there is any linear correlation between gross and other numeric variables that we have
library(corrplot)
#Based on the scatterplots, we could see some linear correlation between gross and imdb_score, num_critic_for_reviews, num_user_for_reviews, movie_facebook_like
pairs(gross ~ duration + budget + imdb_score + num_critic_for_reviews + num_user_for_reviews + movie_facebook_likes + director_facebook_likes + actor_1_facebook_likes + actor_2_facebook_likes + actor_3_facebook_likes + cast_total_facebook_likes, data = moviedata)

#Correlation Matrix -- There is moderate correlation between gross and num_critic_for_reviews, num_user_for_reviews, and somewhat correlation between gross and cast_total_facebook_likes, movie_facebook_like. Also, there is some colinearity between the variables. 
corrplot(round(cor(subset(moviedata, select=c(gross, duration, budget, imdb_score, num_critic_for_reviews, num_user_for_reviews, movie_facebook_likes, director_facebook_likes, actor_1_facebook_likes, actor_2_facebook_likes,actor_3_facebook_likes, cast_total_facebook_likes))),2), method="circle")
```

#### Feature Engineering Step 1  -- recode genres into 1/0 colums

```{r}
#The dataset had all genres combined as a string. Hence, we need to recode the genres into different column as 1/0 for further analysis.
moviedata$genres_action<- ifelse(grepl("Action", moviedata$genres)==TRUE, 1,0)
moviedata$genres_adventure<- ifelse(grepl("Adventure", moviedata$genres)==TRUE, 1,0)
moviedata$genres_animation<- ifelse(grepl("Animation", moviedata$genres)==TRUE, 1,0)
moviedata$genres_biography<- ifelse(grepl("Biography", moviedata$genres)==TRUE, 1,0)
moviedata$genres_comedy<- ifelse(grepl("Comedy", moviedata$genres)==TRUE, 1,0)
moviedata$genres_crime<- ifelse(grepl("Crime", moviedata$genres)==TRUE, 1,0)
moviedata$genres_documentary<- ifelse(grepl("Documentary", moviedata$genres)==TRUE, 1,0)
moviedata$genres_drama<- ifelse(grepl("Drama", moviedata$genres)==TRUE, 1,0)
moviedata$genres_family<- ifelse(grepl("Family", moviedata$genres)==TRUE, 1,0)
moviedata$genres_fantasy<- ifelse(grepl("Fantasy", moviedata$genres)==TRUE, 1,0)
moviedata$genres_film_noir<- ifelse(grepl("Film-Noir", moviedata$genres)==TRUE, 1,0)
moviedata$genres_game_show<- ifelse(grepl("Game-Show", moviedata$genres)==TRUE, 1,0)
moviedata$genres_history<- ifelse(grepl("History", moviedata$genres)==TRUE, 1,0)
moviedata$genres_horror<- ifelse(grepl("Horror", moviedata$genres)==TRUE, 1,0)
moviedata$genres_music<- ifelse(grepl("Music", moviedata$genres)==TRUE, 1,0)
moviedata$genres_musical<- ifelse(grepl("Musical", moviedata$genres)==TRUE, 1,0)
moviedata$genres_mystery<- ifelse(grepl("Mystery", moviedata$genres)==TRUE, 1,0)
moviedata$genres_news<- ifelse(grepl("News", moviedata$genres)==TRUE, 1,0)
moviedata$genres_reality_tv<- ifelse(grepl("Reality-TV", moviedata$genres)==TRUE, 1,0)
moviedata$genres_romance<- ifelse(grepl("Romance", moviedata$genres)==TRUE, 1,0)
moviedata$genres_sci_fi<- ifelse(grepl("Sci-Fi", moviedata$genres)==TRUE, 1,0)
moviedata$genres_short<- ifelse(grepl("Short", moviedata$genres)==TRUE, 1,0)
moviedata$genres_sport<- ifelse(grepl("Sport", moviedata$genres)==TRUE, 1,0)
moviedata$genres_thriller<- ifelse(grepl("Thriller", moviedata$genres)==TRUE, 1,0)
moviedata$genres_war<- ifelse(grepl("War", moviedata$genres)==TRUE, 1,0)
moviedata$genres_western<- ifelse(grepl("Western", moviedata$genres)==TRUE, 1,0)
```

#### Feature engineering step 2  -- recode plot_keywords into 1/0 colums

We added 18 frequently appeared keywords from plot_keywords column of our dataset.
Those frequently appeared keywords are generated through text mining.

#### Feature engineering step 2  -- plot_keywords -- text mining on all data

```{r}
library(tm) 
#delete those have missing values in plot_keywords
movie_tm <- moviedata[moviedata$plot_keywords != "", ]

#split the plot_keywords and add each word into the keywords list
keywords <- c()
i <- 1
for (ins in movie_tm$plot_keywords){
  kw <- strsplit(ins, "[|]")
  if (length(kw) != 0){
    for (word in kw[[1]]){
      if (!(word %in% keywords)){
        keywords[i] <- word
        i = i + 1
      }
    }
  }
}

#text mining, remove the normal words
corpus <- VCorpus(VectorSource(keywords)) #save text into corpus
corpus <- tm_map(corpus, PlainTextDocument, lazy = T) # creat a plain text document
corpus<-tm_map(corpus,removeWords,stopwords(kind="en"))
corpus <- tm_map(corpus, removeWords, c("base",'camera','fall','movie','tv','film','charact','and', 'in', 'of', 'the', 'on','to', 'title','reference','female','male','by','man','woman','year'))
corpus <- tm_map(corpus, removeWords, c("based","character","star"))

tdm <- TermDocumentMatrix(corpus,
                          control = list(wordLengths = c(1, Inf)))
term.freq <- rowSums(as.matrix(tdm))
term.freq <- subset(term.freq, term.freq >= 2)
df <- data.frame(term = names(term.freq), freq = term.freq,stringsAsFactors=FALSE)
df_sorted <- df[order(-df$freq),]

df_sorted[rownames(df_sorted)=='new',]$term <- "new york"
rownames(df_sorted[rownames(df_sorted)=='new',]) <- "new york"

#plot the most frequent words
library(ggplot2)
p <- ggplot(df_sorted[1:10,], aes(x=term, y=freq,fill=freq)) + geom_bar(stat="identity") +
  xlab("Keywords")  + ylab("Frequency")+coord_flip()
p +labs( y = "Keywords", x = "Frequency") +
  theme_bw() + 
  theme(legend.position = "None") 

#Wordcloud
library(wordcloud2)
figPath = system.file("examples/t.png",package = "wordcloud2")
wordcloud2(df_sorted,figPath = figPath, size = 1.5,color="random-dark")
```

From the previous text mining on the whole dataset, we found that sex, war, car, school, relationship, american, death, child, new york, police is the top 10 frequently appear words in plotline keywords.

#### Feature engineering step 2  -- plot_keywords -- text mining on top 250 gross movies

```{r}
#subset the top250 gross data
movie_data_sorted <- movie_tm[order(-movie_tm$gross),]
movie_topgross <- subset(movie_tm,movie_tm$gross>=movie_data_sorted[250,]$gross)

#split the plot_keywords and add each word into the keywords list
keywords <- c()
i <- 1
for (ins in movie_topgross$plot_keywords){
  kw <- strsplit(ins, "[|]")
  if (length(kw) != 0){
    for (word in kw[[1]]){
      if (!(word %in% keywords)){
        keywords[i] <- word
        i = i + 1
      }
    }
  }
}

#text mining, remove the normal words
corpus <- VCorpus(VectorSource(keywords)) #save text into corpus
corpus <- tm_map(corpus, PlainTextDocument, lazy = T) # creat a plain text document
corpus<-tm_map(corpus,removeWords,stopwords(kind="en"))
corpus <- tm_map(corpus, removeWords, c("base",'camera','fall','movie','tv','film','charact','and', 'in', 'of', 'the', 'on','to', 'title','reference','female','male','by','man','woman','year'))
corpus <- tm_map(corpus, removeWords, c("based","character","star"))

tdm <- TermDocumentMatrix(corpus,
                          control = list(wordLengths = c(1, Inf)))
term.freq <- rowSums(as.matrix(tdm))
term.freq <- subset(term.freq, term.freq >= 5)
df <- data.frame(term = names(term.freq), freq = term.freq,stringsAsFactors=FALSE)
df_sorted <- df[order(-df$freq),]

#plot the most frequent words
p <- ggplot(df_sorted[1:10,], aes(x=term, y=freq,fill=freq)) + geom_bar(stat="identity") +
  xlab("Keywords")  + ylab("Frequency")+coord_flip()
p +labs( y = "Keywords", x = "Frequency") +
  theme_bw() + 
  theme(legend.position = "None") 

#Wordcloud
term.freq <- rowSums(as.matrix(tdm))
term.freq <- subset(term.freq, term.freq >= 1)
df <- data.frame(term = names(term.freq), freq = term.freq,stringsAsFactors=FALSE)
df_sorted <- df[order(-df$freq),]
figPath = system.file("examples/t.png",package = "wordcloud2")
wordcloud2(df_sorted,shape="diamond", size = 1.5,color="random-dark")

```

From the previous text mining on movies that have the top 250 gross data, we found that car, relationship, space, father, hero, death, fairy, animal, alien, and agent are the top 10 frequently appeared keywords.

The keywords in top 250 gross data was so different from keywords in the whole dataset. The difference in keywords maybe can explain the difference in final gross, so we added all those frequently appeared keywords as our variables and wanted to see whether they can actually make a difference.

```{r}
#add 18 plot_keywords
moviedata$keywords_space <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "space", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_space<- 1

moviedata$keywords_relationship <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "relationship", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_relationship <- 1

moviedata$keywords_hero <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "hero", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_hero <- 1

moviedata$keywords_father <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "father", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_father <- 1

moviedata$keywords_fairy <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "fairy", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_fairy<- 1

moviedata$keywords_death <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "death", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_death <- 1

moviedata$keywords_car <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "car", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_car <- 1

moviedata$keywords_animal <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "animal ", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_animal  <- 1

moviedata$keywords_alien <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "alien", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_alien <- 1

moviedata$keywords_agent <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "agent", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_agent <- 1

moviedata$keywords_war <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "war", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_war <- 1

moviedata$keywords_school <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "school", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_school <- 1

moviedata$keywords_police <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "police", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_police <- 1

moviedata$keywords_nudity <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "nudity", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_nudity<- 1

moviedata$keywords_american <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "american", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_american <- 1

moviedata$keywords_sex <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "sex", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_sex <- 1

moviedata$keywords_girl <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "girl", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_girl <- 1

moviedata$keywords_child <- 0
moviedata[moviedata[["plot_keywords"]] %in% grep(pattern = "child", x = moviedata[["plot_keywords"]], value = TRUE), ]$keywords_child <- 1
```

#### Feature engineering step 3  -- recode content_rating into 1/0 colums

```{r}
library(caret)
dmy <- dummyVars(~content_rating,data=moviedata)
dmydf <- data.frame(predict(dmy,newdata=moviedata))
moviedata <- cbind(moviedata,dmydf)
```

#### Feature engineering step 4  -- recode country lanuage into 1/0 colums

```{r}
#country language
moviedata$isenglish[moviedata$language == "English"] <- 1
moviedata$isenglish[moviedata$language != "English"] <- 0
moviedata$isusa[moviedata$country == "USA"] <- 1
moviedata$isusa[moviedata$country != "USA"] <- 0
#3235 movies from USA
sum(moviedata$isusa, na.rm=TRUE)
```

#### Feature engineering step 5  -- recode color into 1/0 colums

```{r}
#country language
summary(moviedata$color)
moviedata$isColor[moviedata$color == "Color"] <- 1
moviedata$isColor[moviedata$color != "Color"] <- 0
```

#### Finished data cleaning and feature engineering process

We may not use all the variables generated from our data cleaning process.
We choose variables based on our purpose and our model.

```{r}
cleanedmoviedata <- moviedata
str(cleanedmoviedata)
colnames(cleanedmoviedata)
```

#### Feature selection

We then turned many categorical variables into 1/0 format, so that we could fit the model's requirements. 

After the feature engineering process, we have 93 features:
isColor, director_name, num_critic_for_reviews, duration, director_facebook_likes, actor_3_facebook_likes, actor_2_name, actor_1_facebook_likes, gross, genres, actor_1_name, movie_title, num_voted_users, cast_total_facebook_likes, actor_3_name, facenumber_in_poster, plot_keywords, movie_imdb_link, num_user_for_reviews, language, country, content_rating, budget, title_year, actor_2_facebook_likes, imdb_score, aspect_ratio, movie_facebook_likes, genres_action, genres_adventure, genres_animation, genres_biography, genres_comedy, genres_crime, genres_documentary, genres_drama, genres_family, genres_fantasy, genres_film_noir, genres_game_show, genres_history, genres_horror, genres_music, genres_musical, genres_mystery, genres_news, genres_reality_tv, genres_romance, genres_sci_fi, genres_short, genres_sport, genres_thriller, genres_war, genres_western, keywords_space,keywords_relationship, keywords_hero, keywords_father, keywords_fairy, keywords_death, keywords_car, keywords_animal, keywords_alien, keywords_agent, keywords_war, keywords_school, keywords_police, keywords_nudity, keywords_american, keywords_sex, keywords_girl, keywords_child, content_rating., content_rating.Approved, content_rating.G, content_rating.GP, content_rating.M, content_rating.NC.17, content_rating.Not.Rated, content_rating.Passed, content_rating.PG, content_rating.PG.13, content_rating.R, content_rating.TV.14, content_rating.TV.G, content_rating.TV.MA, content_rating.TV.PG, content_rating.TV.Y, content_rating.TV.Y7, content_rating.Unrated, content_rating.X, isenglish, isusa

We needed to choose which features to include in each of our models

##### Feature selection1 -- Random Forest
Random Forest is not only a good way to make predictions but also a good way to select features because it will tell us the importance order of features.

```{r}
library(randomForest)
#random forest has a limitation, it cannot run on categorical variables which has more than 53 variables, so first we have to subset our data.
#random forest also not allow predictors have any NA values.
movie_fs = subset(cleanedmoviedata, select = c(isColor, num_critic_for_reviews, duration, director_facebook_likes, actor_3_facebook_likes, actor_1_facebook_likes, num_voted_users, cast_total_facebook_likes, facenumber_in_poster, num_user_for_reviews, budget, title_year, actor_2_facebook_likes, imdb_score, aspect_ratio, movie_facebook_likes, genres_action, genres_adventure, genres_animation, genres_biography, genres_comedy, genres_crime, genres_documentary, genres_drama, genres_family, genres_fantasy, genres_film_noir, genres_game_show, genres_history, genres_horror, genres_music, genres_musical, genres_mystery, genres_news, genres_reality_tv, genres_romance, genres_sci_fi, genres_short, genres_sport, genres_thriller, genres_war, genres_western, keywords_space,keywords_relationship, keywords_hero, keywords_father, keywords_fairy, keywords_death, keywords_car, keywords_animal, keywords_alien, keywords_agent, keywords_war, keywords_school, keywords_police, keywords_nudity, keywords_american, keywords_sex, keywords_girl, keywords_child, content_rating.Approved, content_rating.G, content_rating.GP, content_rating.M, content_rating.NC.17, content_rating.Passed, content_rating.PG, content_rating.PG.13, content_rating.R, content_rating.TV.14, content_rating.TV.G, content_rating.TV.MA, content_rating.TV.PG, content_rating.TV.Y, content_rating.TV.Y7, content_rating.X, isenglish, isusa))
rf <- randomForest(movie_fs,cleanedmoviedata$gross,ntree=100,importance=TRUE,proximity = TRUE)
importance(rf)
varImpPlot(rf)
```

From random forest, we can know the 28 important variables in predicting gross is:
budget, imdb_score, title_year, isusa, isenglish,duration,aspect_ratio,
num_user_for_reviews, num_voted_users, num_critic_for_reviews 
cast_total_facebook_likes, movie_facebook_likes,director_facebook_likes, actor_1_facebook_likes,actor_2_facebook_likes,actor_3_facebook_likes,
genres_family, genres_drama, genres_crime, genres_horror, genres_comedy, genres_adventure,genres_thriller, genres_sci_fi
content_rating.R,content_rating.PG.13, content_rating.PG
keywords_sex,

##### Feature selection2 -- Lasso Regression

```{r}
library(glmnet)
x <- model.matrix(cleanedmoviedata$gross ~ ., movie_fs)[,-1]
y <- cleanedmoviedata$gross
grid <- 10 ^ seq(10,-2,length=100)
lasso.mod <- glmnet(x,y, alpha=1,lambda = grid)
cv.out <- cv.glmnet(x, y,alpha=1)
bestlam <- cv.out$lambda.min
out <- glmnet(x,y,alpha=1,lambda = grid)
lasso.coef <- predict(out, type='coefficients',s=bestlam)[1:ncol(movie_fs),]
lasso.coef[lasso.coef!=0]
```

From best lambda lasso regression, 58 variables have none zero coefficients.
Still too much variables, we increase the lambda.

```{r}
lasso.coef <- predict(out, type='coefficients',s=0.06)[1:ncol(movie_fs),]
lasso.coef[lasso.coef!=0]
```

With 0.1 lambda lasso regression, 18 variables have no zero coefficients:
isColor, num_critic_for_reviews, duration, num_voted_users, cast_total_facebook_likes , num_user_for_reviews, title_year, actor_2_facebook_likes, genres_action, genres_animation, genres_comedy, genres_documentary, genres_drama, genres_family, genres_film_noir, content_rating.G, content_rating.PG, content_rating.PG.13

With 0.06 lambda lasso regression, 25 variables have no zero coefficients,
The additional non zero coefficients are :
movie_facebook_likes, genres_biography, genres_mystery,genres_sci_fi, genres_thriller,  keywords_sex, content_rating.R 

##### Feature selection3 -- best fit, forward, backward

```{r}
library(leaps)
movie_subset = subset(cleanedmoviedata, select = c(gross, 
isColor, num_critic_for_reviews, duration, director_facebook_likes, actor_3_facebook_likes, actor_1_facebook_likes, num_voted_users, cast_total_facebook_likes, facenumber_in_poster, num_user_for_reviews, budget, title_year, actor_2_facebook_likes, imdb_score, aspect_ratio, movie_facebook_likes, genres_action, genres_adventure, genres_animation, genres_biography, genres_comedy, genres_crime, genres_documentary, 
genres_drama, genres_family, genres_fantasy, genres_film_noir, genres_game_show, genres_history, genres_horror, genres_music, genres_musical, genres_mystery, genres_news, genres_reality_tv, genres_romance, genres_sci_fi, genres_short, genres_sport, genres_thriller, genres_war, genres_western,
keywords_space,keywords_relationship, keywords_hero, keywords_father, keywords_fairy, keywords_death, keywords_car, keywords_animal, keywords_alien, keywords_agent, keywords_war, keywords_school, keywords_police, keywords_nudity, keywords_american, keywords_sex, keywords_girl, keywords_child, content_rating.Approved, content_rating.G, content_rating.GP, content_rating.M, content_rating.NC.17, content_rating.Passed, content_rating.PG, content_rating.PG.13, content_rating.R, content_rating.TV.14, content_rating.TV.G, content_rating.TV.MA, content_rating.TV.PG, content_rating.TV.Y, content_rating.TV.Y7, content_rating.X, isenglish, isusa))
reg.seqrep <- regsubsets(gross~., data = movie_subset, nvmax = 20, nbest = 1, method = "seqrep")
plot(reg.seqrep, scale = "adjr2", main = "Adjusted R^2")
summary(reg.seqrep)
```

Features recommemded by the hybrid approach is: 
isColor, duration, title_year, aspect_ratio
isusa, isenglish,
num_critic_for_reviews,
cast_total_facebook_likes, movie_facebook_likes, director_facebook_likes
genres_action,  genres_comedy, genres_drama, genres_family, genres_thriller,
genres_sci_fi, 
content_rating.G, content_rating.PG,content_rating.PG.13,content_rating.R,



According to the result of random forest, lasso regression and hybrid of forward and backward method, we decide to choose the following features to conduct our model analysis :

#### 26 feature advised to be selected:

isColor, duration, title_year, budget, aspect_ratio,imdb_score,
isusa, isenglish,
num_voted_users, num_user_for_reviews, num_critic_for_reviews,
cast_total_facebook_likes, movie_facebook_likes,  director_facebook_likes
genres_action,  genres_comedy, genres_drama, genres_family, genres_sci_fi,  genres_thriller, 
content_rating.G, content_rating.PG, content_rating.PG.13,content_rating.R,
keywords_sex, keywords_space

They may exist serious multicollinearity.

#### Selected feature data: 26 features

```{r}
selected_movie = subset(cleanedmoviedata, select = c(gross, 
isColor, duration, title_year, budget, aspect_ratio,imdb_score,
isusa, isenglish,
num_voted_users, num_user_for_reviews, num_critic_for_reviews,
cast_total_facebook_likes, movie_facebook_likes, director_facebook_likes,
genres_action,  genres_comedy, genres_drama, genres_family, genres_sci_fi,  genres_thriller, 
content_rating.G, content_rating.PG, content_rating.PG.13,content_rating.R,
keywords_sex, keywords_space))
str(selected_movie)
```

However, we still found some problems with our dataset.

#### Multicollinearity ? Yes

```{r}
library(car)
fit <- lm(gross ~., data = selected_movie)
summary(fit)
vif(fit)
cor(selected_movie)

# num_voted_users / num_user_for_reviews / num_critic_for_reviews are highly correlated
# we decide to combine num_user_for_reviews and num_critic_for_reviews 
selected_movie$num_reviews = selected_movie$num_user_for_reviews + selected_movie$num_critic_for_reviews

# content_rating.PG  content_rating.PG.13  content_rating.R are highly correlated
# create a new varible content_rating_new according to the restrictive level
selected_movie$content_rating_new <- 0
selected_movie$content_rating_new[selected_movie$content_rating.PG == 1] <- 1
selected_movie$content_rating_new[selected_movie$content_rating.PG.13 == 1] <- 2
selected_movie$content_rating_new[selected_movie$content_rating.R == 1] <- 3

# remove the highly correlated columns
selected_movie = subset(selected_movie, select = c(
- num_voted_users, - num_user_for_reviews, - num_critic_for_reviews,
- content_rating.G, - content_rating.PG, - content_rating.PG.13))
```

#### Scaling problem ? Yes

```{r}
# the maximum numbers of different continuous variables have huge differences.
apply(selected_movie, 2, min);
apply(selected_movie, 2, max);
# the maximun of budget is 1.221550e+10 compared to 1 the maximun of most dummy variable 
# we need to scale the dependent variables.
selected_movie$budget = scale(selected_movie$budget)
selected_movie$cast_total_facebook_likes = scale(selected_movie$cast_total_facebook_likes)
selected_movie$movie_facebook_likes = scale(selected_movie$movie_facebook_likes)
selected_movie$director_facebook_likes = scale(selected_movie$director_facebook_likes)
selected_movie$num_reviews = scale(selected_movie$num_reviews)
```

### Model Selection process

```{r}
finalmoviedata <- selected_movie
str(finalmoviedata)
colnames(finalmoviedata)
```


#### Split train and test Set

```{r}
set.seed(1000)
movie_sample <- sample(2, nrow(finalmoviedata), replace=TRUE, prob=c(0.67, 0.33))
movie_train <- finalmoviedata[movie_sample==1, ] # contain gross
movie_test <- finalmoviedata[movie_sample==2, ] # contain gross
#Now we need to create our 'Y' variables 
movie.trainY <- finalmoviedata[movie_sample==1, "gross"]
movie.testY <- finalmoviedata[movie_sample==2, "gross"]
```


### Linear Regression Model Selection

#### Model Selection
  After multiple rounds of testing, below is our selected model for predicting a movie gross income. All predictors are significant with a decent R-squared 0.38 and a low RSE. Furthermore, F statstics returns a small p-value means that our model is significant. 

```{r}
model.bestfit <- lm(gross~ isColor + duration + isusa + isenglish + cast_total_facebook_likes  + genres_action + genres_comedy + genres_drama + genres_family + genres_sci_fi + genres_thriller + num_reviews, data = movie_train)

summary(model.bestfit)
```

#### Checking model reliability
We wants do perform some tests to see how reliable our model is.
##### Checking Residual plot
Our residual plots show that the model is passable. There is a good scatter of the residuals around the zero for the range of fitted values. The residuals Q-Q Plot shows a somewhat abnormal distribution but mimics the left-hand skewed of the original gross sale.

However, Durbin Watson test with a small autocorrelation value indicates that there is some autocorrelation issue with our model.

```{r}
par(mfrow=c(2,2))
plot(model.bestfit)

library(car)
durbinWatsonTest(model.bestfit)
```

### Application of our model - We expect to use our model to predict gross sale of a movie based on its characteristics
If we were the executives of a studio, we would want to create a model to predict the gross sale of a movie based on its characteristics prior to its release, or even prior to production to make a decision before investment.

```{r}
library(Metrics)
gross_predict <- predict(model.bestfit, movie_test)
scatterplot(movie_test$gross, gross_predict)
rmse(movie_test$gross,gross_predict)
sqrt(mean(residuals(model.bestfit)^2))
min(finalmoviedata$gross)
max(finalmoviedata$gross)
```

Scatter plot shows that our predictions are close to the real value. Plus, Our RMSEs from the model and test dataset are similiar and our RMSEs are small comparing to the range of our gross values.

However, our dependent variable was log-transformed to decrease the skewness. Therefore, we would want to convert log-transformed value back to real gross value and compare the results.

```{r}
movie_test$gross_orig <- exp(movie_test$gross)
movie_test$gross_predict <- exp(predict(model.bestfit, movie_test))

summary(movie_test$gross_orig)
summary(movie_test$gross_predict)
rmse(movie_test$gross_orig,movie_test$gross_predict)

```

We got an interesting result here where mean of predict gross is higher than its 3rd quartile. This indicates that there are extreme outliers in our predictions. The skewed nature of the original gross income and high RMSE could be the reasons for this issue.

Unfortunately, we don't have a reliable model to predict movie gross sale.

###Conclusion
Overall, we weren't able to create a reliable model to predict movie gross sale. However, through the process of creating our model, we were able to see some correlations between movie gross sales and some characteristics. Therefore, we think that it is possible to predict movie sale based on certain characteristics with a more complex data handling skills.

### Limitations and Future Improvement

####Limitations
One of the limitations that we encountered was the data availability. The data we derived from imdb had missing values which meant we had to remove/ replace them by using the mean values to replace the missing values. 

Another limitation was that table did not take into account monetary inflation between 1920 (the earliest produced movie in the dataset) and 2016 (the most recent movie data). A 10 millions profit back in 1920 would be valued differently in 2016. 

####Future Improvements
One of the improvements that we could think of is that if we could scrap the data from multiple sources to compare and fill in the missing information, we could improve the reliability of the model. We could also taken inflation into consideration, further subsetting the data, or add more variables into the model.

Other improvements we could implement is that we could try different methods to remove autocorrelation in our model or try other different regression methods such as PCR, Random Forest, Lasso Regression or even Exponential Regression.




